Quasicharacters and the function-sheaf dictionary

### 2014-09-07 crelle-dictionary.tex
Fixed references to Tate's thesis, stacks project.

Let $R$ be the ring of integers of $K$.
Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$ for every non-negative integer $n$.
Suppose $X_K \in \mathcal{N}_K$ has N\'eron model $X$ over $R$.
Note that $X(K) = X(R)$.
A \emph{quasicharacter of $X(K)$} is a group homomorphism $X(K) \to \EEx$ that factors through $X(R) \to X(R_n)$ for some non-negative integer $n$.
We note that this use of the term is compatible with the use of the term {\it quasicharacter} in \cite{Cassels-Frohlich:ANT}*{Ch XV, \S 2.3}.
 \todo{add bibliography entry for Tate's thesis}
The group of quasicharacters of $X(K)$ will be denoted by 
\[
\Hom_\text{qc}(X(K),\EEx)
\]
 and the subgroup of those that factor through $X(R_n)$ will be denoted by 
 \[
 \Hom_n(X(K),\EEx).
\]
In this section we will see how to geometrize and categorify quasicharacters of $X(K)$ using quasicharacter sheaves.

@@

For any $n\leq m$,  the surjective ring homomorphism $R_{m} \to R_n$ determines a
natural transformation 
\[
\varrho^R_{n\leq m} : \Gr^R_{m} \to \Gr^R_n
\]
between additive functors.
Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
This observation is key to the proof that, for any scheme $X$ over $R$, the projective limit 
\[
\Gr_R(X) \ceq \varprojlim_{n\in \NN} \Gr^R_n(X),
\]
taken with respect to the surjective morphisms $\varrho^R_{n\leq m}(X) : \Gr^R_{m}(X) \to \Gr^R_n(X)$,
exists in the category of group schemes over $\Fq$;
see \cite{stacks_project:limits}*{Lem 2.2}.
\todo{add bibliography entry for the Stacks project}
This leads to the definition of what we shall call the {\it Greenberg transform}:
\[
\Gr_R : \Sch{R} \to \Sch{\Fq}.
\]
By construction, the $\Fq$-scheme $\Gr_R(X)$ comes equipped with morphisms 
\[
\varrho^R_n(X) : \Gr^R(X) \to \Gr^R_n(X),\qquad \forall n\in \NN.
\]

>>>>

Let $R$ be the ring of integers of $K$.
Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$ for every non-negative integer $n$.
Suppose $X_K \in \mathcal{N}_K$ has N\'eron model $X$ over $R$.
Note that $X(K) = X(R)$.
A \emph{quasicharacter of $X(K)$} is a group homomorphism $X(K) \to \EEx$ that factors through $X(R) \to X(R_n)$ for some non-negative integer $n$.
We note that this use of the term is compatible with the use of the term {\it quasicharacter} in \cite{cassels-frohlich:AlgebraicNumberTheory}*{Ch XV, \S 2.3}.
The group of quasicharacters of $X(K)$ will be denoted by 
\[
\Hom_\text{qc}(X(K),\EEx)
\]
 and the subgroup of those that factor through $X(R_n)$ will be denoted by 
 \[
 \Hom_n(X(K),\EEx).
\]
In this section we will see how to geometrize and categorify quasicharacters of $X(K)$ using quasicharacter sheaves.

@@

For any $n\leq m$,  the surjective ring homomorphism $R_{m} \to R_n$ determines a
natural transformation 
\[
\varrho^R_{n\leq m} : \Gr^R_{m} \to \Gr^R_n
\]
between additive functors.
Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
This observation is key to the proof that, for any scheme $X$ over $R$, the projective limit 
\[
\Gr_R(X) \ceq \varprojlim_{n\in \NN} \Gr^R_n(X),
\]
taken with respect to the surjective morphisms $\varrho^R_{n\leq m}(X) : \Gr^R_{m}(X) \to \Gr^R_n(X)$,
exists in the category of group schemes over $\Fq$;
see \cite{stacks-project}*{Limits of Schemes, Lem 2.2}.
This leads to the definition of what we shall call the {\it Greenberg transform}:
\[
\Gr_R : \Sch{R} \to \Sch{\Fq}.
\]
By construction, the $\Fq$-scheme $\Gr_R(X)$ comes equipped with morphisms 
\[
\varrho^R_n(X) : \Gr^R(X) \to \Gr^R_n(X),\qquad \forall n\in \NN.
\]
